VISUALIZATION OF THE RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL

### 2019-09-25 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
added more sections

\section{Left-sided Riemann-Liouville Fractional Integral}
In this section we review the definition of the left-sided Riemann-Liouville fractional integral of order $\alpha$ (based at $a'$) \cite{laurent1884}. Please note that in this paper from this point going forward our variable of integration will be $\tau$ instead of $x$. It is our opinion that this notational change improves the readability of the paper. Let
\begin{equation}
_{a'}I_t\, f(t) := \int_{a'}^t f(\tau)~d\tau.
\end{equation}
If we apply the above operator in a repetitive manner to $f$ we obtain the $n$th antiderivative of $f$ based at $a'$:
\begin{equation}
\label{eq:n_anti}
_{a'}I_t^n\,f(t) = \int_{a'}^t\int_{a'}^{\tau_1}\cdots \int_0^{\tau_{n-1}}f(\tau_n)~d\tau_n\cdots d\tau_2 d\tau_1.
\end{equation}
Applying Cauchy's repetitive integration formula to Eq.~\eqref{eq:n_anti} results in:
\begin{equation}
\label{eq:cauchy}
_{a'}I_t^n\,f(t) = \frac{1}{(n-1)!}\int_0^t (t-\tau)^{n-1}f(\tau)~d\tau.
\end{equation}
As an example if $f(t)=t$, $n=2$ and $a'=0$ then Eq.~\eqref{eq:cauchy} reduces to:
\begin{equation}
_{0}I_t^2\,f(t) = \int_0^t (t-\tau)\tau~d\tau = \frac{\tau^2 t}{2} - \frac{\tau^3}{3} \Bigg |_0^t = \frac{t^3}{3!}.
\end{equation}
The definition in Eq.~\eqref{eq:cauchy} can now be extended to an arbitrary fractional order by replacing $(n-1)!$ with the Gamma function (see Fig.~\ref{fig:gamma}):
\begin{equation}
\label{eq:frac_integral}
_{a'}I_t^{\alpha}f(t) = \frac{1}{\Gamma(\alpha)}\int_{a'}^t (t-\tau)^{\alpha-1}f(\tau)~d\tau.
\end{equation}
Eq.~\eqref{eq:frac_integral} is known as the left-sided Riemann-Liouville fractional integral of order $\alpha$. As an example if $f(t)=t$, $\alpha=\frac{1}{2}$ and $a'=0$ then 
Eq.~\eqref{eq:frac_integral} reduces to:
\begin{equation}
_0 I_t^{\frac{1}{2}}\,f(t) = \frac{1}{\Gamma(\frac{1}{2})} \int_0^t \frac{\tau}{\sqrt{t-\tau}} d\tau = \frac{1}{\sqrt{\pi}}\left [ -\frac{2}{3}\sqrt{t-\tau}(2t+\tau)\right] \Bigg |_0^t=\frac{4}{3\sqrt{\pi}}t^{\frac{3}{2}}. 
\end{equation}

@@

>>>>

\section{Left-sided Riemann-Liouville Fractional Integral}
In this section we review the definition of the left-sided Riemann-Liouville fractional integral of order $\alpha$ (based at $a'$) \cite{laurent1884}. Let
\begin{equation}
_{a'}I_t\, f(t) := \int_{a'}^t f(\tau)~d\tau.
\end{equation}
Please note that in this paper from this point going forward our variable of integration will be $\tau$ instead of $x$. It is of our opinion that this notational change improves the readability of the paper (if $\tau$ is our variable of integration then it makes sense to choose $t$ to denote our upper integration limit in Eq.~\ref{??}). 
If we apply the above operator in a repetitive manner to $f$ we obtain the $n$th antiderivative of $f$ based at $a'$:
\begin{equation}
\label{eq:n_anti}
_{a'}I_t^n\,f(t) = \int_{a'}^t\int_{a'}^{\tau_1}\cdots \int_0^{\tau_{n-1}}f(\tau_n)~d\tau_n\cdots d\tau_2 d\tau_1.
\end{equation}
Applying Cauchy's repetitive integration formula to Eq.~\eqref{eq:n_anti} results in:
\begin{equation}
\label{eq:cauchy}
_{a'}I_t^n\,f(t) = \frac{1}{(n-1)!}\int_0^t (t-\tau)^{n-1}f(\tau)~d\tau.
\end{equation}
As an example if $f(t)=t$, $n=2$ and $a'=0$ then Eq.~\eqref{eq:cauchy} reduces to:
\begin{equation}
_{0}I_t^2\,f(t) = \int_0^t (t-\tau)\tau~d\tau = \frac{\tau^2 t}{2} - \frac{\tau^3}{3} \Bigg |_0^t = \frac{t^3}{3!}.
\end{equation}
The definition in Eq.~\eqref{eq:cauchy} can now be extended to an arbitrary fractional order by replacing $(n-1)!$ with the Gamma function (see Fig.~\ref{fig:gamma}):
\begin{equation}
\label{eq:frac_integral}
_{a'}I_t^{\alpha}f(t) = \frac{1}{\Gamma(\alpha)}\int_{a'}^t (t-\tau)^{\alpha-1}f(\tau)~d\tau.
\end{equation}
Eq.~\eqref{eq:frac_integral} is known as the left-sided Riemann-Liouville fractional integral of order $\alpha$. As an example if $f(t)=t$, $\alpha=\frac{1}{2}$ and $a'=0$ then 
Eq.~\eqref{eq:frac_integral} reduces to:
\begin{equation}
_0 I_t^{\frac{1}{2}}\,f(t) = \frac{1}{\Gamma(\frac{1}{2})} \int_0^t \frac{\tau}{\sqrt{t-\tau}} d\tau = \frac{1}{\sqrt{\pi}}\left [ -\frac{2}{3}\sqrt{t-\tau}(2t+\tau)\right] \Bigg |_0^t=\frac{4}{3\sqrt{\pi}}t^{\frac{3}{2}}. 
\end{equation}

@@

\section{Geometric Interpretation of the Left-sided Riemann-Liouville Fractional Integral}

\subsection{Converting into a Riemann-Stieltjes integral}
Podlubny showed that the Left-sided Riemann-Liouville fractional integral can be rewritten as a Riemann-Stieltjes integral \cite{podlubny02}:
\begin{theorem}
The following integrals are equivalent
\begin{equation}
_{a'}I_t^{\alpha}\,f(t) = \frac{1}{\Gamma(\alpha)}\int_{a'}^{t}(t-\tau)^{\alpha-1}f(\tau)~d\tau = \int_{a'}^{t} f(\tau)~dg_t^{\alpha}(\tau), 
\end{equation}
with 
\begin{equation}
\label{eq:g_rl}
g_t^{\alpha}(\tau) = \frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)}. 
\end{equation}
\end{theorem}

\begin{proof}
Note that 
\begin{equation}
\label{eq:diff}
\frac{dg_t^{\alpha}(\tau)}{d\tau} = \frac{\alpha(t-\tau)^{\alpha-1}}{\Gamma(\alpha+1)} =\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)}. 
\end{equation}
Furthermore,
\begin{equation}
\label{eq:inter_step}
\int_{a'}^{t} f(\tau)\,dg_t^{\alpha}(\tau) = \int_{a'}^{t} f(\tau) \frac{dg_t^{\alpha}(\tau)}{d\tau}\,dg_t^{\alpha}(\tau). 
\end{equation}
The desired result is obtained by substituting Equation~\eqref{eq:diff} into Equation~\eqref{eq:inter_step}.  
\end{proof}

In this section we present a novel geometric interpretation of the Riemann-Liouville fractional integral. 
Recall that the Riemann-Liouville fractional integral of order $\alpha$ is defined as:
\begin{equation}
\label{eq:RL_frac_int}
\frac{1}{\Gamma(\alpha)}\int_{0}^{t}f(\tau)(t-\tau)^{\alpha-1}~d\tau
\end{equation}

\noindent
Podlubny showed that the above fractional integral can be rewritten as a Riemann-Stieltjes integral \cite{podlubny02}:
\begin{equation}
\label{eq:rs}
\int_0^{t} f(\tau)~dg_t(\tau),
\end{equation}
with 
\begin{equation}
\label{eq:g_rl}
g_t^{\alpha}(\tau) = \frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)}. 
\end{equation}

\noindent
Note that $g_t^{\alpha}(\tau)$ is always invertible, since $\frac{d g_t^{\alpha}}{d \tau} = \frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)}>0$ for $\tau\in[0,t]$. The inverse 
of $g_t^{\alpha}(\tau)$ is equal to:
\begin{equation}
h_t^{\alpha}(\tau) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)\tau}
\end{equation}

\noindent
Let $\mathsf{A} = \{0,0.2,0.4,0.6,0.8,1\}$. The analytic expressions of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ are presented in Table~\ref{tab:gandh} for $\alpha\in\mathsf{A}$. 
The expressions in Table~\ref{tab:gandh} are depicted in Fig~\ref{fig:gandh}.

\begin{table}[h!]
 \centering
 \caption{The analytic expressions of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$.}
 \label{tab:gandh}
 \begin{tabular}{|c || c | c|} 
 \hline
 $\alpha$ & $g_{10}^{\alpha}(\tau)$ & $h_{10}^{\alpha}(\tau)$ \\ [0.5ex] 
 \hline\hline
 $0$ & 0 & $y=0$ \\ 
 $0.2$ & $[\Gamma\left (\frac{6}{5} \right )]^{-1}\left(\sqrt[5]{10}-\sqrt[5]{10-\tau}\right)$ & $10 - \left ( \sqrt[5]{10} -  \Gamma\left (\frac{6}{5} \right ) \tau \right )^5$  \\
 $0.4$ & $[\Gamma\left (\frac{7}{5} \right )]^{-1}\left(\sqrt[5]{10^2}-\sqrt[5]{(10-\tau)^2}\right)$ & $10 - \sqrt{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{7}{5} \right ) \tau \right )^5}$ \\
 $0.6$ & $[\Gamma\left (\frac{8}{5} \right )]^{-1}\left(\sqrt[5]{10^3}-\sqrt[5]{(10-\tau)^3}\right)$ & $10 - \sqrt[3]{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{8}{5} \right ) \tau \right )^5}$ \\
 $0.8$ & $[\Gamma\left (\frac{9}{5} \right )]^{-1}\left(\sqrt[5]{10^4}-\sqrt[5]{(10-\tau)^4}\right)$ & $10 - \sqrt[4]{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{9}{5} \right ) \tau \right )^5}$ \\ [1ex] 
 $1$ & $\tau$ & $\tau$ \\ [1ex] 
 \hline
 \end{tabular}
 \end{table}

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{gh.pdf}
\caption{This figure depicts the curves of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$. The curves associated with $g$ are plotted using 
solid lines, while the curves plotted with dashed lines are associated with $h$. The lighter the shade with which a curve is depicted, the larger the $\alpha$-value is that is associated with it.
}
\label{fig:gandh}
\end{figure}

\noindent
Furthermore, Grobler showed that it is trivial to convert a Riemann-Stieltjes integral into a Cavalieri integral \cite{ackermann12,grobler19} (see Fig.~\ref{fig:caval2} and the Cavalieri section of this paper if more details are required). If we apply Grobler's conversion method to Eq.~\eqref{eq:rs} we obtain:
\begin{equation}
\label{eq:cav}
\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau, 
\end{equation}
with
\begin{equation}
\label{eq:cav_a}
a_t^{\alpha}(y) = f^{-1}(y) - \frac{t^{\alpha}-(t-f^{-1}(y))^{\alpha}}{\Gamma(\alpha+1)}.
\end{equation}
Eq.~\eqref{eq:cav_a} is obtained by substituting Eq.~\eqref{eq:g_rl} into Eq.~\eqref{eq:a_y}. Note, $b_t^{\alpha}(y) = a_t^{\alpha}(y) + \frac{t^{\alpha}}{\Gamma(\alpha+1)}$.

\noindent
We can now assign a geometric interpretation to Eq.~\eqref{eq:cav}, since it is a Cavalieri integral (see Fig.~\ref{fig:caval2} and the Cavalieri section of this paper). The fractional integral in Eq.~\eqref{eq:RL_frac_int} can, therefore, be interpreted as the area obtained 
by summing together the area of an infinite number of infinitesimally small non-rectangular integration strips whose shape is determined by $\alpha$ and $t$. If $\alpha$ is equal to one, however, then the integral reduces to a normal Riemann integral as the integration strips become rectangular for this particular choice of $\alpha$ (its shape becomes independent of $t$).\\

\noindent
Interestingly, Eq.~\eqref{eq:main_cav} implies that we can use $h_t^{\alpha}(\tau)$ to convert Eq.~\eqref{eq:cav} into the following Riemann integral:
\begin{equation}
\label{eq:option2}
\int_0^{\frac{t^{\alpha}}{\Gamma(\alpha+1)}} f\circ h_{\alpha}^t (\tau) d\tau.  
\end{equation}
We can, therefore, evaluate Eq.~\eqref{eq:cav} in one of two ways: we can either evaluate Eq.~\eqref{eq:rs} or we can evaluate Eq.~\eqref{eq:option2}.
